Make the full map of Tanzania land cover

### 2022-02-27 docs/tanzania_full_map.Rmd
Subset images for North

```{r}
move_train <- lapply(1:nrow(north_train), function(n) {
    things_to <- unlist(north_train[n, c("label", 'img')])
    things_from <- gsub("train", "dl_train", things_to)
    things_to <- file.path(here("results/tanzania"), things_to)
    things_from <- file.path(here("results/north"), things_from)
    file.copy(things_from, things_to)
})

move_valid <- lapply(1:nrow(north_valid), function(n) {
    things_to <- unlist(north_valid[n, c("label", 'img')])
    things_from <- gsub("validation", "dl_valid", things_to)
    things_to <- file.path(here("results/tanzania"), things_to)
    things_from <- file.path(here("results/north"), things_from)
    file.copy(things_from, things_to)
})
```

>>>>

```{r}
library(terra)
# Select features
load(here('data/tanzania/forest_vip.rda'))
var_selected <- data.frame(var = names(forest_vip$fit$variable.importance),
                           imp = forest_vip$fit$variable.importance) %>% 
  filter(str_detect(var, c('band')) | # remove indices
           str_detect(var, c('vv')) |
           str_detect(var, c('vh'))) %>% 
  filter(imp > 1000) # remove less important ones

move_train <- lapply(1:nrow(north_train), function(n) {
    # Label, directly copy
    things_to <- north_train[n, 'label']
    things_from <- gsub("train", "dl_train", things_to)
    things_to <- file.path(here("results/tanzania"), things_to)
    things_from <- file.path(here("results/north"), things_from)
    file.copy(things_from, things_to)

    # Image, subset it
    things_to <- north_train[n, 'img']
    things_from <- gsub("train", "dl_train", things_to)
    things_to <- file.path(here("results/tanzania"), things_to)
    things_from <- file.path(here("results/north"), things_from)

    sat <- rast(things_from)
    sat <- subset(sat, var_selected$var)
    writeRaster(sat, things_to, overwrite = TRUE)
})

move_valid <- lapply(1:nrow(north_valid), function(n) {
    # Label, directly copy
    things_to <- north_valid[n, "label"]
    things_from <- gsub("validation", "dl_valid", things_to)
    things_to <- file.path(here("results/tanzania"), things_to)
    things_from <- file.path(here("results/north"), things_from)
    file.copy(things_from, things_to)

    # Image, subset it
    things_to <- north_valid[n, "img"]
    things_from <- gsub("validation", "dl_valid", things_to)
    things_to <- file.path(here("results/tanzania"), things_to)
    things_from <- file.path(here("results/north"), things_from)
    sat <- rast(things_from)
    sat <- subset(sat, var_selected$var)
    writeRaster(sat, things_to, overwrite = TRUE)
})
```
